\input{../def.tex}

\begin{document}

\avantgarde

\section{Paradox of $\pi$\,?}

I wrote down the four paradoxes
about love, measurement, solar eclipses and decoherence
earlier today,
while almost all ideas go back way longer.
%
I have purposely left many things open in those earlier articles,
in the hope
to maybe spur the imagination of readers a bit more,
and also because I might rather be interested in different things
than pursuing them in the future.

My official take on this “fifth” paradox
is that it is just wild speculation:
{\color{xphi}Long-range “telepathic” connections
with polarized spin 1 symmetry,
passing unperturbed through any matter,
mediated maybe by selective perception
of virtual photons or the like\,?}
%
Unofficially, “eppur si muove”?

Such connections,
especially between two lovers,
would be felt most strongly
if both persons would look into the direction of each other
or into opposite directions,
and gradually less strongly if not.
%
Also, the feeling would be maximal
if the symmetry planes of their heads would be aligned,
e.g.\ if both were lying
with their heads in the same direction or any opposite ones,
and gradually weaker if not.*
%
The feeling would get weaker with more distance between the two,
but apparently not decay quadratically with distance,
and no matter in between,
not even earth itself,
would make a clear difference.
%
The explanation might be that virtual photons,
or maybe other spin 1 bosons,
would mediate the felt connection,
hence the symmetry of polarized light.

\vspace{2mm}
\noindent
Adliswil, 19 October 2018 {\tiny \color{xphi}$\pi$.}

\vspace{5mm}
\noindent
{\footnotesize
* Say, A and P are standing opposite each other, facing each other, their heads upright.
Then the feeling is maximal.
Now A starts to turn around slowly, the head still upright and in the direction of the body.
The feeling will get weaker, be weakest at 90°, then get stronger again and be practically maximal again at 180°, then get weaker again, weakest at 270°, and get stronger again towards 0° again.
Now A tilts the head to the right, the feeling will get weaker, be again minimal at 90°, then A stands on the head, 180°, where the feeling will be practically maximal again, and then back to minimal at 270° and back to maximal at 0°.\par}

\end{document}
