\input{../def.tex}

\begin{document}

\avantgarde

\section{Paradox of love}

{\color{xphi}Is love a real connection between two lovers\,?}
%
Any direct connection becomes physically impossible
according to current science
as soon as two lovers separate a few miles
(and do not use technical devices to communicate).
%
Is love thus just a mutual illusion
that exists only separately in the two lovers,
maybe even when they are physically together\,?
%
The answer is both, in a way, as follows.

The human brain mirrors much of the outside world on the inside,
in order to be able to communicate with the outside world
and to predict how things will behave.
%
This includes especially loved ones,
which are mirrored much more intensively
and in more detail than most other beings and things outside.
%
Since this mirroring usually does not mean
that everything is analytically understood,
but is mainly just mirrored by “training the neural networks” in the brain,
the mirror image of a loved one
allows also to predict things about a loved one
that neither person is consciously aware of,
nor even that it would be stored 
in some analytically structured form in their two brains at all.

In network technology,
there is the term of a {\color{xphi}\textsl{store-and-forward}} network,
a network where there are no permanent connections,
but data is stored at each node
and exchanged whenever the connection becomes available again.
%
In the case of the two lovers,
they would, of course,
talk to each other and exchange themselves with all of their senses
as soon as they meet again after having been separated,
say, during the day at work.
%
But a store-and-forward network is still a network,
as long as there is repeated exchange.

Hence you could at least qualitatively explain
why, say, the loved one called you on the phone
just when you were thinking about him or her, etc.
%
You would have simply mirrored each other so closely,
that similar thoughts and feelings
would have occurred to both of you at the same time.

But it goes even further:
Connecting two brains in such a way effectively creates a larger brain,
potentially a larger being, the “relationship”,
with maybe its own thoughts, dreams, feelings, and so on.
%
This is likely why relationships can never be fully understood by the two lovers,
simply because they really “go over your head”,
as they involve two heads,
and the dynamics between them is impossible to fully grasp for a single brain.

All in all,
some aspects of a relation can never be changed,
you only have the possibility to stay in it or leave it,
or maybe change the dynamics by adding new elements,
like when you have children,
which then also become part of a larger complex of brains,
the family, in this case.

{\color{xphi}In conclusion,
love would be a real connection,
but not be permanently synchronized,
unless yet unconfirmed new physics would still allow it.}

\end{document}
