\input{../def.tex}

\begin{document}

\avantgarde

\section{Discoveries revisited}

In 2002, I published a 29 page article titled “A few new discoveries in physics”
plus a single page review on this web site.
%
I still think that the document is an important contribution to the world
and that some of its quirks should be overlooked
in order not to miss the opportunities.
%
But this is\,“your beer”$\!$.

\vspace{2mm}
\href{https://www.exactphilosophy.net/discoveries.zip}{\color{xphi}\underline{discoveries.zip}}

\subsection{Contents of discoveries.zip}

\begin{list}{$\bullet$}{\setlength{\leftmargin}{13pt}}
\item discoveries.pdf 
– The main 29 page document,
including also the May 2001 disclosure with proof of discovery in the appendix.
\vspace{-2mm}
\item discoveries-hires.pdf
– The same document at higher resolution (2019).
\vspace{-2mm}
\item more/discoveries.txt
– The plain text of discoveries.pdf.
\vspace{-2mm}
\item more/review.pdf
– My single page review of 31 March 2002.
\vspace{-2mm}
\item more/fewmore.pdf
– Timeline of when I wrote which parts of discoveries.pdf
(plus an earlier philosophical text).
\vspace{-2mm}
\item more/wei-chi.pdf
– A usenet post from 2004 (posted to alt.test).
\vspace{-2mm}
\item more/disclosures/
– Several earlier discovery disclosures from 1998 to 2001,
plus a document that shows how I published
(now cryptographically somewhat outdated)
proofs of discovery at the time.
\vspace{-2mm}
\item more/odyssey.pdf
– Short document with a quote from Usenet.
\vspace{-2mm}
\item more/pages
– All pages of discoveries.pdf at their native resolution of 300 dpi (dvi-ps-pdf toolchain),
plus review.pdf also rendered at 300 dpi.
\vspace{-2mm}
\item more/sources
– Original La\negthinspace TeX source of discoveries.pdf.
\vspace{-2mm}
\item more/sources-hires
– La\negthinspace TeX source of discoveries.pdf minimally adapted in 2019;
renders to same line and page breaks,
but on pixel level there are tiny differences,
most notably space between main text and footnotes.
\vspace{-2mm}
\item more/fewmore-hires.pdf
– Higher resolution and color chart (2019).
\vspace{-2mm}
\item more/source-fewmore-hires
– Corresponding La\negthinspace TeX source.

\end{list}

\end{document}