\input{../def.tex}

% strong title "font"
\contournumber{16}
\contourlength{0.2pt}
\newcommand{\widen}{\hspace{0.27pt}}

\begin{document}

\avantgarde

\ttfamily
\Large
\noindent
\contour{black}{u\widen s\widen e\widen n\widen e\widen t
o\widen d\widen y\widen s\widen s\widen e\widen y}

\footnotesize
\vspace{4mm}
\noindent
Usenet is (or rather was) like a gigantic theater play, staged by millions of
actors without any script. Trying to extract just my lines from that complex
and scintillating web of possibilities would maybe destroy a lot of that, and
even then I would have to leave out a *lot*, so that the best possible result
would be something that would not differ all that much from the main contents
of my website exactphilosophy.net or of my artecat.ch books?

\vspace{2mm}
\noindent
Anyway, for the moment just "follow the white rabbit" of my usenet posts from
June 2002 until roughly 2009, in various usenet newsgroups and with different
email addresses. Most of my posts are no longer archived at Google Groups at
my requests around ten years ago, but other usenet archives still carry them.

\vspace{2mm}
\noindent
Looks like I might maybe never extract fragments from usenet, because I don\textquotesingle t
want to take things apart? Thanks everyone in usenet for all the fish!\ :)

\vspace{2mm}
\noindent
Leave these islands in the usenet ocean? It\textquotesingle s still all there!

\vspace{2mm}
\noindent
Me early Pisces 2004 at alt.astrology.tropical:

\vspace{2mm}
\noindent
:~In life, because one often would have the option\newline
:~to say or do more than one finally does and can\newline
:~do, the things that one does not say or not do,\newline
:~are more important than the ones that are done.

\vspace{2mm}
\noindent
)o+

\end{document}
