\input{../def.tex}

\begin{document}

\avantgarde

\section{Web archives}

Some selected archive copies of this website in the past.

Just download the respective zip file,
unzip it and open index.html in your favorite web browser.

Plus free pdf book downloads where archives correspond to printed books.

\subsection{Web 2005}

Early \LaTeX/fox icon version,
of late December 2005,
with already the main idea in sections
\textsl{space and time}, \textsl{metamorphosis}, \textsl{greek philosophy} and \textsl{i ching}.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2005.zip}{\color{xphi}\underline{web2005.zip}}

\subsection{Web 2009}

Richer in content (but also of more varying quality)
than most versions before and after until about 2015.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2009.zip}{\color{xphi}\underline{web2009.zip}}

\begin{list}{$\bullet$}{\setlength{\leftmargin}{13pt}}
%
\item \textbf{architecture} – Click on my email on the top-left corner
for separate overviews for readers coming from science, astrology or philosophy.
\vspace{-2mm}
%
\item \textbf{elementary philosophy} and the \textbf{first subsection of evolutions}
– Basically the same fundamental idea about describing elements in terms of in/out and rest/move
as is still the foremost topic on my website today (2016).
\vspace{-2mm}
\item \textbf{long-range feelings}
– Various considerations around the nature and potential range of feelings
and how that could potentially explain many phenomena in this world quite uniformly.
\vspace{-2mm}
\item \textbf{elementary star signs}
– My model of the star signs in terms of transformations between the four greek elements.
\vspace{-2mm}
\item \textbf{magic carpets}
– An explanation of my general method of association for exploring symbolic worlds
and some applications involving astrology and ancient Chinese culture.
\vspace{-2mm}
\item \textbf{moebius lego}
 – A text that I would now (2016) classify as some kind of precognition
 of my explorations of “the moon” that followed in 2010, in two versions,
 one possibly typed only with my left hand.
\vspace{-2mm}
\item \textbf{reflectivity} – Some rumination on science and my personal odyssey.

\end{list}

\subsection{Web 2016}

This website 5 August 2016,
as in the book \textsl{exactphilosophy.net 2016}.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2016.zip}{\color{xphi}\underline{web2016.zip}} \ \
\href{https://www.exactphilosophy.net/noindex/books/xphi2016.pdf}{\color{xphi}\underline{web2016.pdf}}

\vspace{4mm}
\noindent
Features the first publication of my arrangement of the 8 trigrams of the I Ching
as 8 transitions between the four elements in Aristotle’s circle.

\subsection{Web 2017}

This website early December 2017,
as in the book \textsl{exactphilosophy.net 2017}.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2017.zip}{\color{xphi}\underline{web2017.zip}} \ \
\href{https://www.exactphilosophy.net/noindex/books/xphi2017.pdf}{\color{xphi}\underline{web2017.pdf}}

\vspace{4mm}
\noindent
Features many refinements and new leads in the web pages,
a careful article about the 8 trigrams of the I Ching
as 8 transitions between the four elements in Aristotle’s circle,
or even arranged on a Möbius strip,
and more.

\subsection{Web 2019}

This website May 2019,
as in the book \textsl{exactphilosophy.net 2019}.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2019.zip}{\color{xphi}\underline{web2019.zip}} \ \
\href{https://www.exactphilosophy.net/noindex/books/xphi2019.pdf}{\color{xphi}\underline{web2019.pdf}}

\vspace{4mm}
\noindent
Labeled ‘the definitive edition’ at the time here,
which has some truth to it,
but it also introduced some quite core errors
that were only amended again later.

\subsection{Web 2020}

This website early November 2020,
as in the book \textsl{exactphilosophy.net 2020}.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2020.zip}{\color{xphi}\underline{web2020.zip}} \ \
\href{https://www.exactphilosophy.net/noindex/books/xphi2020.pdf}{\color{xphi}\underline{web2020.pdf}}

\vspace{4mm}
\noindent
Tiny advances at the most vital spots, and some more;
see the article \textsl{Babysteps 2019 2020}
for a graphical exposure of a few key differences.

\subsection{Web 2020 ste \hspace{-0.1em}\normalsize{1st Edition}}

This website, without articles,
as in the book \textsl{Space, Time, Elements at exactphilosophy.net}.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2020-ste1.zip}{\color{xphi}\underline{web2020-ste1.zip}} \ \
\href{https://www.exactphilosophy.net/noindex/books/ste1-2020.pdf}{\color{xphi}\underline{ste1-2020.pdf}}

\vspace{4mm}
\noindent
Idea that what the psyche does and experiences
would be essentially along the circle of elements.

\subsection{Web 2021 ste \hspace{-0.1em}\normalsize{2nd Edition}}

This website, without articles,
as in the book \textsl{Space, Time, Elements at exactphilosophy.net},
Second Edition.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2021-ste2.zip}{\color{xphi}\underline{web2021-ste2.zip}} \ \
\href{https://www.exactphilosophy.net/noindex/books/ste2-2021.pdf}{\color{xphi}\underline{ste2-2021.pdf}}

\vspace{4mm}
\noindent
Several new findings:
Heavy/light from in/out and rest/move,
Apuleius’ tasks of Psyche related to Plato,
archaic psyche 3+1.
%
Site mobile-friedly.

\subsection{Web 2021 rich}

This website before streamlining articles.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2021-rich.zip}{\color{xphi}\underline{web2021-rich.zip}}

\vspace{4mm}
\noindent
Details inside.

\subsection{Web 2021}

This website as in the book \textsl{exactphilosophy.net}.

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2021.zip}{\color{xphi}\underline{web2021.zip}} \ \
\href{https://www.exactphilosophy.net/noindex/books/xphi2021.pdf}{\color{xphi}\underline{web2021.pdf}}

\vspace{4mm}
\noindent
Sleeping Beauty Dreaming (2021).

\subsection{Web 2024}

This website as in the book \textsl{exactphilosophy.net} (edition 2024).

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2024.zip}{\color{xphi}\underline{web2024.zip}} \ \
\href{https://www.exactphilosophy.net/noindex/books/xphi2024.pdf}{\color{xphi}\underline{web2024.pdf}}

\vspace{4mm}
\noindent
It is what it is and that is all it is.

\subsection{Web 2025}

This website as in the book \textsl{exactphilosophy.net} (final edition 2025).

\vspace{2mm}
\href{https://www.exactphilosophy.net/web2025.zip}{\color{xphi}\underline{web2025.zip}} \ \
\href{https://www.exactphilosophy.net/noindex/books/xphi2025.pdf}{\color{xphi}\underline{web2025.pdf}}

\vspace{4mm}
\noindent
But if the little fox…

\end{document}
