\input{../def.tex}

\begin{document}

\avantgarde

\section{Amber’s seen and not Heard prank\,?}

I guess pretty much everybody heard the story
about something Amber Heard supposedly would have left on the bed
of her then husband Johnny Depp
on the night of her 30\hspace{0.05em}th birthday
or the morning after,
21/22 April 2016.
%
But I guess nobody got
what exactly the joke was supposed to be
except Amber herself
(\textsl{if} it was really a prank and happened at all),
hence this tiny article…

According to [1],
in the US trial
her younger sister Whitney recalled that
on the evening of Amber’s birthday
the guests took turns mentioning their favorite memory of Amber
and that as part of that Johnny Depp described how Amber
‘came into his office
[in Los Angeles in 2008 for a role in\,\textsl{The Rum Diary}]
and she sat on the couch,
and her perfect ass left a perfect imprint on the couch
and he wouldn’t let anyone sit there after she left that day’.
%
Maybe you have to be a man to see the poetic side in that.
%
It is not reducing her to just her body
(nor particularly to her behind)—%
at least not only that.
%
A shape is more abstract than a literal body and,
maybe a bit like in Pavlov’s experiment,
it can evoke her whole persona,
which seemed to have made quite some impression on Johnny Depp that day.
%
I was not present on the night of her birthday,
and given their apparently frequent arguments in previous months,
it is not sure how exactly he meant it,
but it might actually have been a true expression of this love for her.
%
But I can also see that from the point of view of a woman
it looks different,
is,
as so often,
a much more convoluted matter.

\textsl{\color{xphi}Anyways,
it appears likely to me that Amber
would have decided to show him quite literally
what her behind can do/produce (and not do/produce)
compared to the rest of her persona (body, mind, etc.).}

\vspace{68mm}
\noindent
\footnotesize{[1]
Nick Wallis,
\textsl{Depp v Heard},
Bath Publishing,
2023,
p.\ 143 at the bottom ;).}

\end{document}
